### 2022-01-03 intro.tex
intro

The rest of this paper is structured as follows.

>>>>

The rest of this paper is structured as follows.
\Cref{sec:approach} presents the design principles of the framework.
Next, in \cref{sec:experiments}, we present a series of experiments which validate the utility, flexibility, and repeatability of \ac{CLEAVE}.
Finally, we conclude this paper in \cref{sec:conclusion} with a brief discussion on the strengths and weaknesses of the platform, as well as on future directions to take.
